Sparse Function-space Representation \\ of Neural Networks

### 2023-05-17 paper/main.tex
intro

\textbf{Function-space methods for sequential learning} 
Continual learning (CL) hinges on how to deal with a non-stationary training distribution, wherein the training process may overwrite previously learned parameters, causing catastrophic forgetting \citep{mccloskey1989catastrophic}. CL approaches fall into inference-based, rehearsal-based, and model-based methods (see \cite{parisi2019continual, de2021continual} for an overview). The methods in the first category usually tackle this problem with weight-space regularization, such as EWC~\citep{kirkpatrick2017overcoming}, SI~\citep{zenke17a}), or VCL~\citep{nguyen-tuongModel2009} that induce retention of previously learned information in the weights alone. However, encoding functional knowledge in the weights does not guarantee good quality of the predictions. Function-space regularization techniques~\cite{li2018lwf, benjamin2018measuring, titsias2019functional, buzzega2020dark, pan2020continual, rudner2022continual} address this by relying on training data subsets for each task to compute a regularization term. These methods bridge the gap between objective and rehearsal-based methods \todo{I'm not familiar with the differences between objective vs rehearsal based methods, and it isn't explained here} since they use a subset of the training data for each task to compute the regularization term. Recently proposed methods, \eg, DER~\citep{buzzega2020dark}, FROMP~\citep{pan2020continual}, and S-FSVI~\citep{rudner2022continual} achieve state-of-the-art performance among the objective-based techniques in several CL benchmarks. \todo{Are DER, FROMP and FSVI function-space regularization methods? I assume so but the text makes it a bit vague.}\looseness-2

\textbf{Uncertainty quantification in RL}
A key challenge in RL is balancing the trade-off between exploration and exploitation \cite{sutton2018reinforcement}.
%That is, should an agent select actions that it knows will lead to high reward %(exploitation), or should it
%select new ones in hope to discover actions leading to higher reward (exploration).
One promising direction to balancing this trade-off is to model the uncertainty associated with a learned transition dynamics model and use it to guide exploration.
Prior work has taken an expectation over the dynamic model's posterior \cite{deisenroth2011pilco,kamtheDataEfficient2018,chuaDeepReinforcementLearning2018},
sampled from it (akin to Thompson sampling but referred to as posterior sampling RL)
\todo{cite thopmson sampling paper dearden et al 1999}
\cite{osbandMoreEfficientReinforcement2013},
and used it to implement optimism in the face of uncertainty using upper confidence bounds \cite{curiEfficient2020}.
\todo{cite UCRL paper}
No single strategy has emerged as a go-to method and we highlight that these strategies are only as good as their uncertainty estimates.
Previous approaches have used GPs \cite{deisenroth2011pilco,kamtheDataEfficient2018},
ensembles of neural networks \cite{curiEfficient2020,chuaDeepReinforcementLearning2018}
and variational inference \cite{galImproving2016,houthooftVIME2017}. \todo{Could specify here how the previous methods have used these models}
%However, there has been little leveraging

@@

    GP predictive NN & $1024$ &  \val{97.70}{0.07} & \val{0.080}{0.002} & \val{0.011}{0.001}
                              &  \val{0}{0.07} & \val{0}{0.002} & \val{0}{0.001} \\

    GP predictive & $1024$  & \val{76.28}{1.85} & \val{0.702}{0.029} & \val{0.070}{0.022}
                            & \val{0}{1.85} & \val{0}{0.029} & \val{0}{0.022} \\
    \our NN & $1024$ &  \val{98.02}{0.12} & \val{0.066}{0.003} & \val{0.007}{0.001}
                     &  \val{0}{0.0} & \val{0}{0.003} & \val{0}{0.001} \\
    \our & $1024$ & \val{98.07}{0.06} & \val{0.063}{0.003} & \val{0.005}{0.001}
                  & \val{0}{0.06} & \val{0}{0.003} & \val{0}{0.001} \\
%    \multirow{2}{*}{FMNIST}
%    & MAP & \val{91.39}{0.11} & \val{0.258}{0.004} & \val{0.017}{0.001} \\
    %& BNN predictive \cite{immer2021improving} & \val{84.42}{0.12} & \val{0.942}{0.016} & \val{0.411}{0.008} \\
    % & BNN predictive \cite{ritter2018kfac} & \val{91.20}{0.07} & \val{0.265}{0.004} & \val{0.024}{0.002} \\
    % & GLM predictive \cite{immer2021improving} & \val{92.25}{0.10} & \val{0.244}{0.003} & \val{0.012}{0.003} \\
    %& GP predictive \cite{immer2021improving} $m=3200$ & \val{91.36}{0.11} & \val{0.25}{0.004} & \val{0.007}{0.001} \\
    % & GP predictive NN $m=1024$ &  \val{0}{0.07} & \val{0}{0.002} & \val{0}{0.001} \\
    % & GP predictive $m=1024$  &  \val{0}{1.85} & \val{0}{0.029} & \val{0}{0.022} \\
    % & \our NN $m=1024$ &  \val{0}{0.0} & \val{0}{0.003} & \val{0}{0.001} \\
    % & \our $m=1024$ &  \val{0}{0.06} & \val{0}{0.003} & \val{0}{0.001} \\
    \bottomrule
  \end{tabular}

>>>>

\textbf{Function-space methods for sequential learning} 
Continual learning (CL) hinges on how to deal with a non-stationary training distribution, wherein the training process may overwrite previously learned parameters, causing catastrophic forgetting \citep{mccloskey1989catastrophic}. CL approaches fall into inference-based, rehearsal-based, and model-based methods (see \cite{parisi2019continual, de2021continual} for an overview). The methods in the first category usually tackle this problem with weight-space regularization, such as EWC~\citep{kirkpatrick2017overcoming}, SI~\citep{zenke17a}), or VCL~\citep{nguyen-tuongModel2009} that induce retention of previously learned information in the weights alone. However, regularizing the weights does not guarantee good quality predictions. Function-space regularization techniques~\cite{li2018lwf, benjamin2018measuring, titsias2019functional, buzzega2020dark, pan2020continual, rudner2022continual} address this by relying on training data subsets for each task to compute a regularization term. These methods bridge the gap between objective and rehearsal-based methods \todo{I'm not familiar with the differences between objective vs rehearsal based methods, and it isn't explained here} since they use a subset of the training data for each task to compute the regularization term. Recently proposed methods, \eg, DER~\citep{buzzega2020dark}, FROMP~\citep{pan2020continual}, and S-FSVI~\citep{rudner2022continual} achieve state-of-the-art performance among the objective-based techniques in several CL benchmarks. \todo{Are DER, FROMP and FSVI function-space regularization methods? I assume so but the text makes it a bit vague.}\looseness-2

\textbf{Uncertainty quantification in RL}
A key challenge in RL is balancing the trade-off between exploration and exploitation \cite{sutton2018reinforcement}.
%That is, should an agent select actions that it knows will lead to high reward %(exploitation), or should it
%select new ones in hope to discover actions leading to higher reward (exploration).
One promising direction to balancing this trade-off is to model the uncertainty associated with a learned transition dynamics model and use it to guide exploration.
Prior work has taken an expectation over the dynamic model's posterior \cite{deisenroth2011pilco,kamtheDataEfficient2018,chuaDeepReinforcementLearning2018},
sampled from it (akin to Thompson sampling but referred to as posterior sampling in RL)
\todo{cite thopmson sampling paper dearden et al 1999}
\cite{osbandMoreEfficientReinforcement2013},
and used it to implement optimism in the face of uncertainty using upper confidence bounds \cite{curiEfficient2020}.
\todo{cite UCRL paper}
No single strategy has emerged as a go-to method and we highlight that these strategies are only as good as their uncertainty estimates.
Previous approaches have used GPs \cite{deisenroth2011pilco,kamtheDataEfficient2018},
ensembles of neural networks \cite{curiEfficient2020,chuaDeepReinforcementLearning2018}
and variational inference \cite{galImproving2016,houthooftVIME2017}. \todo{Could specify here how the previous methods have used these models}
%However, there has been little leveraging

@@

    GP predictive NN & $1024$ & \val{97.70}{0.07} & \val{0.080}{0.002} & \val{0.011}{0.001}
                              & \val{91.47}{0.41} & \val{0.289}{0.009} & \val{0.033}{0.003} \\

    GP predictive & $1024$  & \val{76.28}{1.85} & \val{0.702}{0.029} & \val{0.070}{0.022}
                            & \val{83.98}{0.35} & \val{0.503}{0.012} & \val{0.052}{0.006} \\
    \our NN & $1024$ &  \val{98.02}{0.12} & \val{0.066}{0.003} & \val{0.007}{0.001}
                     & \val{91.93}{0.45} & \val{0.267}{0.011} & \val{0.028}{0.003} \\
    \our & $1024$ & \val{98.07}{0.06} & \val{0.063}{0.003} & \val{0.005}{0.001}
                  & \val{91.56}{0.35} & \val{0.253}{0.006} & \val{0.012}{0.001} \\
    \midrule
%    \multirow{2}{*}{FMNIST}
%    & MAP & \val{91.39}{0.11} & \val{0.258}{0.004} & \val{0.017}{0.001} \\
    %& BNN predictive \cite{immer2021improving} & \val{84.42}{0.12} & \val{0.942}{0.016} & \val{0.411}{0.008} \\
    % & BNN predictive \cite{ritter2018kfac} & \val{91.20}{0.07} & \val{0.265}{0.004} & \val{0.024}{0.002} \\
    % & GLM predictive \cite{immer2021improving} & \val{92.25}{0.10} & \val{0.244}{0.003} & \val{0.012}{0.003} \\
    %& GP predictive \cite{immer2021improving} $m=3200$ & \val{91.36}{0.11} & \val{0.25}{0.004} & \val{0.007}{0.001} \\
    % & GP predictive NN $m=1024$ &  \val{0}{0.07} & \val{0}{0.002} & \val{0}{0.001} \\
    % & GP predictive $m=1024$  &  \val{0}{1.85} & \val{0}{0.029} & \val{0}{0.022} \\
    % & \our NN $m=1024$ &  \val{0}{0.0} & \val{0}{0.003} & \val{0}{0.001} \\
    % & \our $m=1024$ &  \val{0}{0.06} & \val{0}{0.003} & \val{0}{0.001} \\
    \bottomrule
  \end{tabular}
